Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
conclusion

In this study, we have investigated a CEGIS-based approach that uses inductive synthesis 
in conjunction with a robust closed-loop stability verification algorithm to find a parametric 
solution for a digital controller given a continuous (or discrete) plant specification.
In particular, we have exploited the automatic synthesis of correct-by-construction 
digital controllers along with a model of their physical environment.
We have also modelled a digital equivalent of the physical plant by evaluating the 
effects of the quantisers (A/D and D/A converters) as time discretisation elements 
with quantisation noise. Experimental results show that our
CEGIS-based approach is able to synthesise stable controllers in most benchmarks
within reasonable time frames.
% and can be 
%complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
%Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
Further studies include the extension of this CEGIS-based approach for different classes of systems
({\it e.g.}, state-space) and also consider performance requirements while synthesising 
the digital controller.

@@

%APPENDICES are optional
%\balancecolumns
%\appendix
%Appendix A
\end{document}

>>>>

We have presented a CEGIS-based approach that uses inductive synthesis in
conjunction with a robust algorithm for verifying closed-loop stability to
compute a parametric solution for a digital controller given a continuous
(or discrete) plant specification.  This enables us to automatically
synthesize correct-by-construction digital controllers for a given model of
their physical environment.  Our approach addresses the effects of the
quantisers (A/D and D/A converters) as time discretisation elements with
quantisation noise.  Our experimental results show that our CEGIS-based
approach is able to synthesise stable controllers in most benchmarks within
reasonable time frames fully automatically.
%
% and can be 
%complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
%Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
%
Future work will be the extension of this CEGIS-based approach for different
classes of systems (e.g., state-space).  We will also consider performance
requirements while synthesising the digital controller.

@@

%APPENDICES are optional
%\balancecolumns
%\appendix
%Appendix A

\end{document}
